Adaptative neigbouring methods applied to telephonic base stations

### 2024-08-14 article.tex
minor modifications

\noindent Each of the precedent methods gives us a list of potential neighbours for each \acrshort{bs}. However, we know that some of this neighbouring connexions are wrong,
because some \acrshort{bs} will be \og hidden\fg{} by others.

Thus, we need to find methods to suppress bad connexions. That was made by Delphine.

The main innovation of our work is to take in account the difference of \acrshort{bs}'s density.

>>>>

\noindent Each of the precedent methods gives us a list of potential neighbours for each \acrshort{bs}. However, we know that some of this neighbouring connexions are wrong,
either because of the neighboring graph construction method or physical specificities linked to the base stations themselves.

Thus, we need to find methods to detetect and erase these bad connexions.

The main innovation of our work compared to this one \cite{art_del_paq} is to take in account the difference of \acrshort{bs}'s density.
